Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
get rid of random These
fixes weird hybrid sentence
removes cruft from editing, "axial"

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{noauthor_gif_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,noauthor_-able_2017,scarlat_design_2014,noauthor_neutronics_2016}. Two
key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together, these attributes result in significantly reduced core fissile
inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  These
Due to these characteristics give the \gls{MSR} potentially unique 
capabilities burning actinides and extending fuel resources.

@@

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profiles are in good agreement. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because axial the \gls{MSRE} design model 
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

>>>>

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{noauthor_gif_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,noauthor_-able_2017,scarlat_design_2014,noauthor_neutronics_2016}. Two
key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together, these attributes result in significantly reduced core fissile
inventories and spent nuclear fuel mass \cite{noauthor_gen_2008}.  
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
burning actinides and extending fuel resources.

@@

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profiles are in good agreement. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because the \gls{MSRE} design model 
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.
